The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-08-07 paper2_JNLS/paper.tex
NM

% ideal, paradigm, canonical, tractable
% ABRUPT depth change

\vsp{4}
Introduce papers: PRF, PNAS, and J Stat Phys. \\

>>>>

The purpose of the present manuscript is to expand on both the experimental findings of Bolles et al.~\cite{bolles2019anomalous} and the theoretical analysis of Majda et al.~\cite{majda2019statistical}, with particular emphasis on the synergy between the two; e.g.~model developments inspired by experimental findings, and new experimental tests inspired by theoretical predictions. We present a range of previously unpublished experimental data, including statistics of the surface {\em slopes} (as opposed to only displacement data as published in \cite{bolles2019anomalous}, autocorrelation data, and some data on experiments in which the depth ratio was varied. We also expand on the theoretical treatment of \cite{majda2019statistical}, with emphasis on more direct link to experiments.

%~experimental discoveries guiding model developments, as well as new theoretical predictions inspiring new experimental tests.

% combination
% draw close comparison
%with an even closer comparison between theoretical predictions and experimental measurements.

\vsp{4}

% ideal, paradigm, canonical, tractable
